---
title: 'Client session analysis '
params:
  prefix: pref
  clientid: 41628
  Year: 2018
  Month: 2017-06
  startMonth: 2017-09
  endMonth: 2017-12
  currency: SEK
  to_divide: 20000
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: true
  html_document: default
  word_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message =  FALSE, results = TRUE )
options(xtable.comment = FALSE)
```

```{r load-packages, message=FALSE, echo=FALSE, warning=FALSE}
if(!require(knitr)){install.packages("knitr")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(lubridate)){install.packages("lubridate")}
if(!require(scales)){install.packages("scales")}
if(!require(tidyr)){install.packages("tidyr")}
#if(!require(gridExtra)){install.packages("gridExtra")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(grid)){install.packages("grid")}
if(!require(xtable)){install.packages("xtable")}
if(!require(reshape2)){install.packages("reshape2")}
if(!require(tibble)){install.packages("tibble")}

```

```{r - utility functions}
source('../utils/functions.R')

```

```{r - required csv}
#weekdaily_yqm_status.csv

```

```{r - global settings}
execute <- TRUE
maxnrofmonth <- 4
status_levels <- c('A', 'O', 'Q', 'R')
colors <- c("total" = "blue", "A" = "#CC3333", "O" = "#009E73", "R" = "#56B4E9", "Q" = "#CC79A7")
colors_browser <- c("Abandonments" = "#CC3333", "Orders" = "#009E73", "Onsites" = "#56B4E9", "Emails" = "#CC79A7")
weekday_levels <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
long_weekday_levels <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
weekday_colors <- c("black", "black", "black", "black", "black", "red", "red")
valueofsales_labels <- c("Weekday", "Direct sales", "Onsite recoveries")
valueofsales_caption <- c("Value of direct sales and onsite recoverie")
avgofsales_caption <- c("Average value of direct sales and onsite recoveries")
yearly_mm_caption <- c("Min, max sessiontimes for weekdays on yearly basis")
yearly_mm_colnames <- c("", "status", "Min", "Max")
yearly_avg_caption <- c("Average sessiontimes for weekdays on yearly basis")
yearly_avg_colnames <- c("", "status", "Avg")
browser_caption <- c("Desktop, mobile browser  traffic for the past 30 days")
browser_caption_summary <- c("Desktop, mobile browser summary on traffic for the past 30 days")
browser_caption_freq <- c("Percentage of desktop, mobile browser  traffic for the past 30 days")
browser_colnames <- c("Desktop", "Mobile")
browser_colnames_orders <- c("Traffic","Abandonments", "Orders", "Onsites", "Emails")

```
\newpage

# Sessiontimes analysis

**Sessiontime summary for clientid = `r params$clientid`**

```{r - title parameters, include=FALSE}
vtitle1.0 = paste("Session times (max, avg, min)")
vsubtitle1.0 = paste(" Client:", params$clientid, "\n",  "Year: ",params$Year)

vtitle1.1="Average Session times on monthly and quarterly basis"
vsubtitle1.1 = paste(" Client:", params$clientid, "\n",  "Year: ",params$Year)

vtitle2 = "Direct sales and Onsite recoveries "
vsubtitle2 = paste(" Client: ",params$clientid, "\n",  "Year: ",params$Year, "\n", "Currency: ",params$currency)
vtitle5 = paste("Desktop, mobile browser traffic for the past 30 days")
vsubtitle51 = paste("Summary for desktop, mobile browser traffic")
vsubtitle52 = paste("Daily trends for desktop, mobile browser traffic")

```




`r vtitle1.0`  
`r vsubtitle1.0`  


```{r - industry temp file, eval=FALSE, include=FALSE}
csvfilepath <- paste("../csv", "/",  "industry.csv", sep = "")
d_industry <- read.csv("industry.csv", header=TRUE, sep=";")
```

```{r - load-csv}
csvfilepath <- paste("../csv", "/",params$prefix,  "weekdaily_yqm_status.csv", sep = "")
d_status <- read.csv(file=csvfilepath, header=TRUE, sep=",")

d_status$clientid <- factor(d_status$clientid)
d_status$Year <- factor(d_status$Year)
d_status$Quarter <- factor(d_status$Quarter)

#order by weekday
d_status$AbrWeekday <- factor(d_status$AbrWeekday, levels= weekday_levels)

```


```{r - count status}
d_count_status <- d_status  %>%
  filter(clientid == params$clientid ) %>%
  group_by(status) %>%
  summarise( NrOfTransactions  = sum(CountOfSessions))

#kable(head(d_count_status))
```


```{r - load extreme sessiontimes csv}
#csvfilepath <- paste("../csv", "/",params$prefix,  "extreme_sessiontimes.csv", sep = "")
#d_extreme_sessiontimes <- read.csv(file=csvfilepath, header=TRUE, sep=",")
#d_extreme_sessiontimes$clientid <- factor(d_extreme_sessiontimes$clientid)

```


```{r - extrem values}
#d_extreme_sessiontimes <- d_extreme_sessiontimes  %>%
#  filter(clientid == params$clientid )

#kable(head(d_extreme_sessiontimes, 20))

```



```{r - yearly}
d_status_yearly <- d_status %>%
  select(everything()) %>% 
  filter(clientid == params$clientid, Year == params$Year, currency == params$currency) %>%
  group_by(status, Weekday, AbrWeekday) %>%
  summarise(AvgSessiontime =  round(mean(AvgSessionTime),0), 
            MinSessiontime = round(min(MinSessionTime),0), 
            MaxSessiontime = round(max(MaxSessionTime),0),
            total = sum(CountOfSessions))

#total nr of transactions as per status
d_status_yearly_total <- d_status_yearly %>%
  select(everything()) %>% 
  group_by(status) %>%
  summarise(total = sum(total))

```




```{r - gather yearly min, max, avg}
gather_d_status_yearly <- d_status_yearly %>% gather(Sessiontimes, Duration, -status,-Weekday, -AbrWeekday, -total)

gather_d_status_yearly$Sessiontimes <- as.factor(gather_d_status_yearly$Sessiontimes)

```


```{r - yearly plot 1 min, max, avg}
# First plot
p_year1 <- ggplot(gather_d_status_yearly, aes(x = AbrWeekday, y = Duration))+ 
  geom_line(aes(x = as.numeric(AbrWeekday), y = Duration, color=factor(Sessiontimes)),  size = 1.2)+
  labs(title = "",
       subtitle = "",
       x = "", 
       y = "Duration in seconds")+
  
  scale_color_discrete(breaks=c("MaxSessiontime","AvgSessiontime","MinSessiontime"))+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = weekday_levels) +
  scale_y_continuous(labels = scales::comma) +
  
  theme(
       axis.title.y = element_text(size = 8),
       legend.title = element_blank(),
       legend.position = "bottom",
       legend.box.margin = unit(c(0, 0, 0, 0), "mm"),
       legend.box.spacing = unit(c(0, 0, 0, 0), "mm"),
       legend.key.height = unit(0.1, "mm"),
       axis.text.x = element_blank(),
       axis.text.y = element_text(face = "bold", size = 7),
       axis.ticks.x = element_line(color = weekday_colors),
       legend.text = element_text(size = 7),
       
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black", size=.2),
       strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
       panel.spacing = unit(1, "lines"),
       plot.margin = unit(c(0, 0, 0, 0), "cm"),
       panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted")) +
#facet_grid(. ~ status)
facet_wrap( ~ status,nrow = 1)

```

```{r - gather yearly min, avg}
gather_d_status_yearly_avg <- d_status_yearly %>% gather(Sessiontimes, Duration, -status,-Weekday, -AbrWeekday, -total, -MaxSessiontime)

gather_d_status_yearly_avg$Sessiontimes <- as.factor(gather_d_status_yearly_avg$Sessiontimes)
```

```{r - yearly plot 1 min avg }
p_year2 <- ggplot(gather_d_status_yearly_avg, aes(x = AbrWeekday, y = Duration))+ 
  geom_line(aes(x = as.numeric(AbrWeekday), y = Duration, color=factor(Sessiontimes)),  size = 1.2)+
  labs(title = "",
       subtitle = "",
       x = "", 
       y = "Duration in seconds")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = weekday_levels) +
  scale_y_continuous(labels = scales::comma) +
  theme(
       axis.title.y = element_text(size = 8),
       legend.title = element_blank(),
       legend.position = "none",
       axis.text.x=element_text(angle=65,hjust=1,vjust=0.5, size = 6,face = "bold",
       color = weekday_colors),
       axis.text.y = element_text(face = "bold", size = 7),
       axis.ticks.x = element_line(color = weekday_colors),
       legend.text = element_blank(),
       
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black", size=.2),
strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
panel.spacing = unit(1, "lines"),
plot.margin = unit(c(0, 0, 0, 0), "cm"),
 panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))+
#facet_grid(. ~ status)
facet_wrap( ~ status,nrow = 1)
  
```

```{r multiplot year 1}
multiplot(p_year1, p_year2, cols = 1)

```

```{r - yearly table summary, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE}
# ordering a dataframe according to a vector
#d_status_yearly <- d_status_yearly[match(weekday_levels, d_status_yearly$AbrWeekday),]
d_status_yearly_A <- d_status_yearly %>%
  select(status, AbrWeekday, MinSessiontime, MaxSessiontime, AvgSessiontime) %>% 
  filter(status == "A")
d_status_yearly_O <- d_status_yearly %>%
  select(status, AbrWeekday, MinSessiontime, MaxSessiontime, AvgSessiontime) %>% 
  filter(status == "O")
d_status_yearly_Q <- d_status_yearly %>%
  select(status, AbrWeekday, MinSessiontime, MaxSessiontime, AvgSessiontime) %>% 
  filter(status == "Q")
d_status_yearly_R <- d_status_yearly %>%
  select(status, AbrWeekday, MinSessiontime, MaxSessiontime, AvgSessiontime) %>% 
  filter(status == "R")

# ordering a dataframe according to a vector
d_status_yearly_A <- d_status_yearly_A[match(weekday_levels, d_status_yearly_Q$AbrWeekday),]
d_status_yearly_O <- d_status_yearly_O[match(weekday_levels, d_status_yearly_O$AbrWeekday),]
d_status_yearly_Q <- d_status_yearly_Q[match(weekday_levels, d_status_yearly_Q$AbrWeekday),]
d_status_yearly_R <- d_status_yearly_R[match(weekday_levels, d_status_yearly_R$AbrWeekday),]
#d_status_yearly_A

df_table <- cbind(d_status_yearly_A, d_status_yearly_O,  d_status_yearly_Q,  d_status_yearly_R)

df_table <- df_table %>% 
  ungroup() %>%
  mutate(status = paste('A', '|','O', '|', 'Q','|', 'R'),
         MinSessiontime = paste(MinSessiontime, MinSessiontime1,MinSessiontime2, MinSessiontime3, sep = '|'),
         MaxSessiontime = paste(MaxSessiontime, MaxSessiontime1,MaxSessiontime2, MaxSessiontime3, sep = '|'),
         AvgSessiontime = paste(AvgSessiontime, AvgSessiontime1,AvgSessiontime2, AvgSessiontime3, sep = '|')) %>%
  select(Weekday, status,MinSessiontime, MaxSessiontime, AvgSessiontime ) 
 
df_table_mm <- df_table %>%
  select(Weekday, status,MinSessiontime, MaxSessiontime )

#renaming back the column to 'Month' names
colnames(df_table_mm) <- yearly_mm_colnames

print(xtable::xtable(df_table_mm, type = "html", caption =  yearly_mm_caption), include.rownames = FALSE, xtable.comment = FALSE)
#kable(df_table_mm, knit.table.format = "html", row.names = FALSE)

```


```{r - yearly plot 2}
y_position <- mean(d_status_yearly$AvgSessiontime)

p1 <- ggplot(d_status_yearly, aes(x = AbrWeekday,y = AvgSessiontime, fill = status)) +
  geom_bar(aes(x = as.numeric(AbrWeekday)), stat='identity', position = "dodge", width = 0.8) +
  #average sessiontimes as text
  #geom_text(data=d_status_yearly_total, 
  #         aes(x=3, y= y_position, label = total),
  #          color='black', fontface = "bold") +
  
  labs( title = "Average Session times on Yearly basis", 
        subtitle = paste(" Client:", params$clientid, "\n",  "Year: ",params$Year),
        x = "", 
        y = "Duration in seconds", 
        caption = "(in the middle - the number of sessions for A, O, P, R statuses)")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = c("Mon","Tue","Wed","Thu","Fri","Sat", "Sun")) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values=colors)+
  theme(axis.text.x=element_text(angle=65,hjust=1,vjust=0.5, size = 7,
       color = weekday_colors),
      axis.ticks.x = element_line(color = weekday_colors), 
      legend.position = "bottom",
      legend.direction =  "horizontal",
      legend.title = element_blank(),
      legend.text = element_text(size = 6),
      strip.text = element_text(face = "bold", size=7,lineheight=5.0),
        strip.background = element_rect(fill="lightblue", colour="black",size=.1),
        axis.text.y=element_text(hjust=1,vjust=0.5, size = 10),
        strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
      panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"),
      plot.title = element_text(hjust = 0.5),
  
      plot.caption = element_text(hjust = 1, size = 8, colour = "gray", face = "italic"))

p1
```

```{r - table summary for yearly average session times, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE}
df_table_avg <- df_table %>%
  select(Weekday, status,AvgSessiontime )

#renaming back the column to 'Month' names
colnames(df_table_avg) <- yearly_avg_colnames

print(xtable::xtable(df_table_avg, type = "html", caption =  yearly_avg_caption), include.rownames = FALSE, xtable.comment = FALSE)

#kable(df_table_a, knit.table.format = "html", row.names = FALSE)

```

\newpage     
**`r vtitle1.1`**       
**`r vsubtitle1.1`**          

```{r - quarterly data}
# for the missing status, quarter, AbrWeekday 0 is added, not to slip the faceting 
d_status_quarterly <- d_status %>%
  select(everything()) %>% 
  filter(clientid == params$clientid, Year == params$Year, currency == params$currency) %>%
  group_by(status, Quarter, AbrWeekday) %>%
  summarise(AvgSessiontime =  round(mean(AvgSessionTime),0), 
            MinSessiontime = min(MinSessionTime), 
            MaxSessiontime = max(MaxSessionTime),
            total = sum(CountOfSessions))

d_status_quarterly$status <- factor(d_status_quarterly$status, levels = status_levels)

# contingency table (freq) on status, Quarter, Abrweekday
qt <- as.data.frame(with (d_status_quarterly, table(status, Quarter, AbrWeekday)))

# df for missing data
qt_zero <- qt %>%
  filter(Freq == 0) %>%
  mutate(AvgSessiontime = 0,
         MinSessiontime = 0,
         MaxSessiontime = 0,
         total = 0) %>%
  select(everything(), -Freq)

# bind rows of the orig df with zeros
d_status_quarterly <- bind_rows(d_status_quarterly, qt_zero)
```


```{r - quarterly plot}
title="Average Session times on Quarterly basis"
subtitle = paste(" Client:", params$clientid, "\n",  "Year: ",params$Year)
x = "Weekday"
y = "Duration in seconds"

p2 <- ggplot(d_status_quarterly, aes(x = AbrWeekday,y = AvgSessiontime,fill= status)) +
  geom_bar(aes(x = as.numeric(AbrWeekday)), stat='identity', position = "dodge", width = 0.8) +
  labs(title="", 
       subtitle = "",
       x = "", 
       y = "") +
  scale_fill_manual(values=colors)+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = weekday_levels) +
  scale_y_continuous(labels = scales::comma) +
  
  theme(axis.text.x=element_text(angle=65,hjust=1,vjust=0.5, size = 6, face = "bold",
       color = weekday_colors),
      axis.ticks.x = element_line(color = weekday_colors), 
      legend.position = "none",
      legend.direction =  "horizontal",
      legend.title = element_blank(),
      legend.text = element_text(size = 6),
      strip.text = element_text(face = "bold", size=7,lineheight=5.0),
      strip.background = element_rect(fill="lightblue", colour="black",size=.1),
      axis.text.y=element_text(hjust=1,vjust=0.5, size = 5.5, face = "bold"),
      strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
      panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted")
      )+
  facet_wrap(Quarter ~ status ,nrow = 4, labeller = label_wrap_gen(multi_line=FALSE), shrink = TRUE)
  
```


```{r - monthly data}
d_status_monthly <- d_status %>%
  select(everything()) %>% 
  filter(clientid == params$clientid, Year == params$Year, currency == params$currency ) %>%
  group_by(status, Month, Weekday, AbrWeekday) %>%
  summarise(AvgSessiontime =  round(mean(AvgSessionTime),0), 
            MinSessiontime = round(min(MinSessionTime),0), 
            MaxSessiontime = round(max(MaxSessionTime),0),
            total = sum(CountOfSessions))

```

```{r - monthly plot}
title="Average Session times on Monthly basis" 
subtitle = paste(" Client:", params$clientid, "\n",  "Year: ",params$Year)

x = "Weekday"
y = "Duration in seconds"

y_position <- mean(d_status_monthly$AvgSessiontime)

p3 <- ggplot(d_status_monthly, aes(x = AbrWeekday,y = AvgSessiontime, fill = status)) +
  geom_bar(aes(x = as.numeric(AbrWeekday)), stat='identity', position = "dodge", width = 0.7) +
  labs( title="", 
        subtitle = "",
        x = "", 
        y = "")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = c("Mon","","","Thu","","", "Sun")) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values=colors)+
  theme(axis.text.x=element_blank(),
       axis.ticks.x = element_line(color = weekday_colors), 
       legend.position = "none",
  
       strip.text = element_text(face = "bold", size=5.5,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black",size=.1),
       axis.text.y=element_text(hjust=1,vjust=0.5, size = 5.5, face = "bold"),
       strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
       panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted")
        )+
  facet_grid( status ~ Month, space="free_y")
 
```

```{r}

  cowplot::ggdraw() +
  cowplot::draw_plot(p2, x = 0, y = 0, width = 1, height = .64) +
  cowplot::draw_plot(p3, x = 0, y = .5, width = 1, height = .63)
  #cowplot::draw_plot_label(label = c("Yearly", "Quarterly", "Monthly"), size = 12, x = c(0, 0.3, 0), y = c(1, 1,.55))

#multiplot(p3, p2, cols = 1)

```

# Value of direct sales, onsite recoveries on monthly and weekdayly basis



```{r data-weekdaily-month-load-csv}
csvfilepath <- paste("../csv", "/",params$prefix,  "weekdaily_month.csv", sep = "")
d_wdm <- read.csv(file=csvfilepath, header=TRUE, sep=",")

d_wdm$clientid <- as.factor(d_wdm$clientid)
d_wdm$Year <- as.factor(d_wdm$Year)

d_wdm$Weekday <- factor(d_wdm$Weekday, levels = long_weekday_levels)

```

```{r weekdaily months, echo = FALSE, message = FALSE, results = TRUE}
d_client_wdm <- d_wdm %>%
  select(clientid, currency, Year, Month, Weekday, ValueOfDirectSales, AvgOfDirectSales, ValueOfOnsiteRecoveries, AvgOfOnsiteRecoveries) %>%
  filter(clientid==params$clientid, Year == params$Year, currency == params$currency)%>%
  arrange(desc(ValueOfOnsiteRecoveries))

#head(d_client_wdm,10)
#tail(d_client_wdm,10)
```


```{r - value and average separation in two tables }
g_d_client_wdm <- d_client_wdm %>% gather(Sales, Value, -clientid, -currency, -Year, -Month, -Weekday)

g_d_client_wdm_sum <- g_d_client_wdm%>%
   filter(!Sales %in% c("AvgOfDirectSales", "AvgOfOnsiteRecoveries"))

g_d_client_wdm_avg <- g_d_client_wdm%>%
   filter(Sales %in% c("AvgOfDirectSales", "AvgOfOnsiteRecoveries"))

```


```{r - direct sales vs Onsite recoveries}
ggplot(g_d_client_wdm_sum, aes(x = as.numeric(Weekday), y = Value, fill = Sales)) +
  geom_bar(stat='identity', width = 0.8)+
  
labs( title = vtitle2,
      subtitle = vsubtitle2,
      x = "", 
      y = "Sales")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = weekday_levels) +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(guide = "legend", labels =  c('direct sales', 'onsite recoveries'), values = c("skyblue", "royalblue"), name= '')+
  
  theme(axis.text.x=element_text(angle=65,hjust=1,vjust=0.5, size = 7, face = "bold",
        color = weekday_colors),
        axis.ticks.x = element_line(color = weekday_colors),
        strip.text = element_text(face = "bold", size=6,lineheight=5.0),
        strip.background = element_rect(colour = "black"),
        legend.position = "bottom", 
        legend.text = element_text(size = 7),
        axis.text.y=element_text(hjust=1,vjust=0.5, size = 7, face = "bold"),
        panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))+
  facet_wrap(~ Month, nrow = row_number_faceting(g_d_client_wdm_sum))

```


```{r - section 2 table format, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE }

table_wdm_sum <- weekday_month_recast(d_client_wdm, 'ValueOfDirectSales', 'ValueOfOnsiteRecoveries', maxnrofmonth)
print(xtable::xtable(table_wdm_sum, type = "html", caption = valueofsales_caption), include.rownames = FALSE, xtable.comment = FALSE)

```


#Average value of direct sales, onsite recoveries on monthly and weekdayly basis

```{r - avg direct sales vs Onsite recoveries}
#TO DO - calculate the nr of months for proper faceting
ggplot(g_d_client_wdm_avg, aes(x = as.numeric(Weekday), y = Value, fill = Sales)) +
  geom_bar(stat='identity', position = "dodge", width = .6)+
  
labs( title = vtitle2,
      subtitle = vsubtitle2,
      x = "", 
      y = "Sales average value")+
  
scale_x_continuous(breaks = c(1,2,3,4,5,6,7), labels = weekday_levels) +
scale_y_continuous(labels = scales::comma) +
scale_fill_manual(guide = "legend", labels =  c('direct sales', 'onsite recoveries'), values = c("skyblue", "royalblue"), name= '')+
  
  theme(axis.text.x=element_text(angle=65,hjust=1,vjust=0.5, size = 7, face = "bold",
       color = weekday_colors),
       axis.ticks.x = element_line(color = weekday_colors),
       strip.text = element_text(face = "bold", size=6,lineheight=5.0),
       strip.background = element_rect(colour = "black"),
       legend.position = "bottom", 
       legend.text = element_text(size = 7),
       axis.text.y=element_text(hjust=1,vjust=0.5, size = 7, face = "bold"),
       panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))+
  facet_wrap(~ Month, nrow = row_number_faceting(g_d_client_wdm_avg$Month))

```

```{r - section 3 table format, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE }

table_wdm_avg <- weekday_month_recast(d_client_wdm, 'AvgOfDirectSales', 'AvgOfOnsiteRecoveries', maxnrofmonth)
print(xtable::xtable(table_wdm_avg, type = "html", caption = avgofsales_caption), include.rownames = FALSE, xtable.comment = FALSE)

```
\newpage
# Customer intensity report

## All status 

```{r - average_json_per_minute}
csvfilepath <- paste("../csv", "/",params$prefix,  "avg_json_per_minute.csv", sep = "")
d_avg_json <- read.csv(file=csvfilepath, header=TRUE, sep=",")

#d_avg_json$clientid <- as.factor(d_avg_json$clientid)

```

```{r - df for intensity}
d_avg_json_real <- d_avg_json %>%
  select(everything()) %>%
  filter(clientid == params$clientid, AvgNrOfJSONsPerMinute>0, maxdelta>=1, AvgNrOfJSONsPerMinute <= 20)%>%
  arrange(desc(AvgNrOfJSONsPerMinute))

# calculating summaries
d_avg_json_summary <- d_avg_json_real %>%
  select(everything()) %>%
  summarise(AvgForClient = round(mean(AvgNrOfJSONsPerMinute),2),
            MaxForClient = max(AvgNrOfJSONsPerMinute))

#calculating the frequency
d_avg_json_freq <- d_avg_json_real %>%
  select(everything()) %>%
  group_by(AvgNrOfJSONsPerMinute)%>%
  summarise(FreqForClient = n())
```


```{r - customer intensity check the existence of dfs}
# in case of empty dfs the next chunk is not executed
dfs <- c(d_avg_json, d_avg_json_real, d_avg_json_summary, d_avg_json_freq)
execute = isempty(dfs) 

```


```{r - histogram of avg nr of jsonns per minute, eval = execute, include = execute}
ggplot(d_avg_json_real, aes(x = AvgNrOfJSONsPerMinute)) +
  geom_bar(width=0.009)+
  geom_vline(data=d_avg_json_summary, aes(xintercept=d_avg_json_summary$AvgForClient), color="blue") +
  geom_text(data=d_avg_json_summary, 
            aes(x= AvgForClient, y=max(d_avg_json_freq$FreqForClient)/2, label =     paste('client ', 'avg','=',AvgForClient)), color='blue', size = 4, angle=90, vjust=-0.4, hjust=0)+
  geom_vline(data=d_avg_json_summary, aes(xintercept=d_avg_json_summary$AvgForClient+3), color="orange") +
  geom_text(data=d_avg_json_summary, 
            aes(x= AvgForClient+3, y=max(d_avg_json_freq$FreqForClient)/2, label =     paste('industry ', 'avg','=',AvgForClient+3)), color='orange', size = 4, angle=90, vjust=-0.4, hjust=0)+

  labs( title = paste("Avg nr of JSONs per Minute for client ", params$clientid), 
      x = "Avg Nr of jsons per minute", 
      y = "Frequency")

  
```


## On statuses ('A_', 'O', 'Q_', 'R_')

```{r - avg json/min on status basis}
csvfilepath <- paste("../csv", "/",params$prefix,  "avg_json_per_minute_with_status.csv", sep = "")
d_avg_json_status <- read.csv(file=csvfilepath, header=TRUE, sep=",")

```

```{r - prepare df for customer intensity on status }
d_avg_json_status_real <- d_avg_json_status %>%
  select(everything()) %>%
  #filter(clientid == params$clientid)%>%
  filter(clientid == params$clientid, AvgNrOfJSONsPerMinute>0, maxdelta>=1, AvgNrOfJSONsPerMinute <= 20)%>%
  arrange(desc(AvgNrOfJSONsPerMinute))

# calculating summary
d_avg_json_status_summary <- d_avg_json_status_real %>%
  select(everything()) %>%
  group_by(status)%>%
  summarise(AvgForClient = round(mean(AvgNrOfJSONsPerMinute),2),
            MaxForClient = max(AvgNrOfJSONsPerMinute))
# calculating frequency
d_avg_json_status_freq <- d_avg_json_status_real %>%
  select(everything()) %>%
  group_by(status, AvgNrOfJSONsPerMinute)%>%
  summarise(FreqForClient = n())
```


```{r - customer intensity status check the existence of dfs}
# in case of empty dfs the next chunk is not executed
dfs <- c(d_avg_json_status, d_avg_json_status_real, d_avg_json_status_summary, d_avg_json_freq)
execute = isempty(dfs) 

```

```{r - histogram of avg nr of jsonns per minute on status basis, eval=execute, include = execute}
ggplot(d_avg_json_status_real, aes(x = AvgNrOfJSONsPerMinute)) +
  geom_bar(width=0.009)+
  geom_vline(data=d_avg_json_status_summary, aes(xintercept=d_avg_json_status_summary$AvgForClient), color="blue") +
  geom_text(data=d_avg_json_status_summary, 
            aes(x= AvgForClient, y=max(d_avg_json_status_freq$FreqForClient)/3, label =     paste('client ', 'avg','=',AvgForClient)), color='blue', size = 3, angle=90, vjust=-0.4, hjust=0)+
  geom_vline(data=d_avg_json_status_summary, aes(xintercept=d_avg_json_status_summary$AvgForClient+3), color="orange") +
  geom_text(data=d_avg_json_status_summary, 
            aes(x= AvgForClient+3, y=max(d_avg_json_status_freq$FreqForClient)/3, label =     paste('industry ', 'avg','=',AvgForClient+3)), color='orange', size = 2, angle=90, vjust=-0.4, hjust=0)+

  labs( title = paste("Avg nr of JSONs per Minute for client ", params$clientid), 
      x = "Avg Nr of jsons per minute", 
      y = "Frequency")+
  facet_wrap( ~ status,nrow = 2)

```
\newpage
#Average daily traffic for the past seven days


```{r - load-csv-past7days}
csvfilepath <- paste("../csv", "/",params$prefix,  "hourly_trafic_7days.csv", sep = "")
d_hourly_traffic <- read.csv(file=csvfilepath, header=TRUE, sep=",")
d_hourly_traffic$clientid <- factor(d_hourly_traffic$clientid)
d_hourly_traffic$Hour <- factor(d_hourly_traffic$Hour)

```


```{r - all traffic status}
d_hourly_traffic_sums <- d_hourly_traffic %>%
  select(everything()) %>% 
  filter(clientid == params$clientid, currency == params$currency) %>%
  group_by(Hour) %>%
  summarise(A =  round(sum(CountOfAbandonments),0), 
            O = round(sum(CountOfDirectSales),0), 
            Q =  round(sum(CountOfOnsiteRecoveries),0), 
            R = round(sum(CountOfEmails),0),
            total = sum(round(sum(CountOfAbandonments),0) +
                        round(sum(CountOfDirectSales),0) +
                        round(sum(CountOfOnsiteRecoveries),0) +
                        round(sum(CountOfEmails),0)  
                          ))
```


```{r - gather past 7 days all}
#all
gather_d_hourly_traffic_sums <- d_hourly_traffic_sums %>% 
  gather(Status, Traffic, -Hour)

```


```{r - all- past 7 days plot}
draw_7daysplot <- function(data, title, colors) {
  ggplot(data, aes(x = Hour, y = Traffic))+
  #ggplot(gather_d_hourly_traffic_sums, aes(x = Hour, y = Traffic))+ 
  geom_line(aes(x = as.numeric(Hour), y = Traffic, color=factor(Status)),  size = 1.2)+
  labs(title = title, 
       subtitle = "",
       x = "Hour", 
       y = "Traffic")+

  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = c(0:24)) +
  scale_color_manual(values=colors)+
  theme(legend.title = element_blank(),
       legend.position = "bottom",
       axis.text.x=element_text(angle=0,hjust=1,vjust=0.5, size = 7),
       legend.text = element_text(size = 8),
       
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black",
size=.2),
strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
panel.spacing = unit(1, "lines"),
panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))
  
}

#All
title <- paste("7 days traffic for client ", params$clientid)
subtitle = paste(" Client: ",params$clientid, "\n",  "Year: ",params$Year, "\n", "Currency: ",params$currency)
x = ""
y = ""
p1 = draw_7daysplot(gather_d_hourly_traffic_sums, "", colors)
p2 = draw_7daysplot(subset(gather_d_hourly_traffic_sums, Status=='A'), title, colors["A"])
p3 = draw_7daysplot(subset(gather_d_hourly_traffic_sums, Status %in% c('O', 'R', 'Q')), "", colors[c("O", "R", "Q")])
#p1
#p2
#p3

multiplot(p2, p1, p3, cols = 2)
  
```
\newpage

# `r vtitle5` 
## `r vsubtitle51`

```{r - load browser type}
csvfilepath <- paste("../csv", "/",params$prefix,  "browser_traffic.csv", sep = "")
df_browser_traffic <- read.csv(file=csvfilepath, header=TRUE, sep=",")
df_browser_traffic$clientid <- factor(df_browser_traffic$clientid)

```

```{r - high level browser summary}
df_browser_summary <- df_browser_traffic %>%
  group_by(browsertype)%>%
  summarise( Transactions  = sum(CountOfSessions),
             Abandonments = sum(CountOfAbandonments),
             Orders = sum(CountOfDirectSales),
             Onsites = sum(CountOfOnsiteRecoveries),
             Emails = sum(CountOfEmails))

#calculate frequency, percentage
df_browser_freq <- data.frame(apply(select(df_browser_summary, 2:6), 2, function(x) x/sum(x)))
#adding the 'browsertype' column to the df in the first place
df_browser_freq <- add_column(df_browser_freq, browsertype = c("D", "M"), .before = 1)
```


```{r gather for plotting summaries}
gather_browser_summary <- df_browser_summary %>%
  gather(Status, Traffic,-browsertype) 

gather_browser_freq <- df_browser_freq %>%
  gather(Status, Traffic,-browsertype) 

gather_browser_orders <- gather_browser_summary %>%
  filter (Status != "Transactions")

gather_browser_all <- gather_browser_summary %>%
  filter (Status == "Transactions")

gather_browser_orders$Status <- factor(gather_browser_orders$Status, levels= c("Abandonments", 
    "Orders", "Onsites", "Emails"))

```

```{r - plot browser summary}
pba <- ggplot(gather_browser_all, aes( x = "", y = Traffic, fill = as.factor(browsertype))) +
  geom_bar(stat = "identity", position = "dodge", width = .4)+
  labs(title = "", 
       subtitle = "",
       x = "", 
       y = "Traffic")+
  scale_fill_manual(label = c("Device", "Mobile"), values = c("blue", "red")) +
  theme(legend.title = element_blank(),
       legend.position = "bottom",
       axis.text.x=element_text(angle=0,hjust=1,vjust=0.5, size = 6),
       legend.text = element_text(size = 8),
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black",
size=.2),
strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
panel.spacing = unit(1, "lines"),
panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))
   

pbo <- ggplot(gather_browser_orders, aes( x = "", y = Traffic, fill = as.factor(Status))) +
  geom_bar(stat = "identity", position = "dodge", width = .6)+
  scale_fill_manual(values = colors_browser) +
  labs(title = "", 
       subtitle = "",
       x = "", 
       y = "")+
  theme(legend.title = element_blank(),
       legend.position = "bottom",
       axis.text.x=element_text(angle=0,hjust=1,vjust=0.5, size = 6),
       legend.text = element_text(size = 8),
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black",
size=.2),
strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
panel.spacing = unit(1, "lines"),
panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))+
   facet_wrap(~ browsertype)
 
multiplot(pba, pbo, cols = 2)

```


```{r browser summary table, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE  }

#renaming the new column names
colnames(df_browser_summary) <- append(as.character(c("")),as.character(browser_colnames_orders))
colnames(df_browser_freq) <- append(as.character(c("")), as.character(browser_colnames_orders))


print(xtable::xtable(df_browser_summary, type = "html", caption = browser_caption_summary), include.rownames = FALSE, xtable.comment = FALSE)  
print(xtable::xtable(df_browser_freq, type = "html", caption = browser_caption_freq), include.rownames = FALSE, xtable.comment = FALSE)


```

## `r vsubtitle52`

```{r daily browser plot function}
browser_plot <- function(data, vy_axis, vy_title, vlegend_position) {
  ggplot(df_browser_traffic, aes(x = Day, y = vy_axis))+
  geom_line(aes(x = as.numeric(Day), y = vy_axis, color=factor(browsertype)),  size = 1.2)+
  labs(title = "", 
       subtitle = "",
       x = "", 
       y = vy_title)+
  scale_x_continuous(breaks = c(0:30)) +
  scale_color_manual(label = browser_colnames, values = c("blue", "red")) +
  theme(legend.title = element_blank(),
       legend.position = vlegend_position,
       axis.text.x=element_text(angle=0,hjust=1,vjust=0.5, size = 6),
       legend.text = element_text(size = 8),
       strip.text = element_text(face = "bold", size=7,lineheight=5.0),
       strip.background = element_rect(fill="lightblue", colour="black",
size=.2),
strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
panel.spacing = unit(1, "lines"),
panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))
  #facet_grid(Status ~ .)
} 

```

```{r - multiplot for browsertype}
bp1 <- browser_plot(df_browser_traffic, df_browser_traffic$CountOfAbandonments, "A","none")
bp2 <- browser_plot(df_browser_traffic, df_browser_traffic$CountOfDirectSales, "O","none")
bp3 <- browser_plot(df_browser_traffic, df_browser_traffic$CountOfOnsiteRecoveries, "Q", "none")
bp4 <- browser_plot(df_browser_traffic, df_browser_traffic$CountOfEmails, "R","bottom")

multiplot(bp1, bp3, bp2, bp4,cols = 2)
```

```{r create summary table, results='asis', echo = FALSE, eval = TRUE, include = TRUE, message = FALSE, warning= FALSE}
table_browser_traffic <- df_browser_traffic %>%
  select(Day, browsertype, CountOfAbandonments,CountOfDirectSales,CountOfOnsiteRecoveries, CountOfEmails)%>%
  recast( Day ~ browsertype  + variable)%>%
  unite(col1, 2:5, sep = "|", remove = TRUE)%>%
  unite(col2, 3:6, sep = "|", remove = TRUE)

#renaming the new column names
colnames(table_browser_traffic) <- append(as.character(c("")), as.character(browser_colnames))

print(xtable::xtable(table_browser_traffic, type = "html", caption = browser_caption), include.rownames = FALSE, xtable.comment = FALSE)  

```

