---
title: 'RFM analysis'
params:
  prefix: pref
  clientid: 50455
  Year: 2017
  Month: 2017-06
  currency: SEK
  to_divide: 20000
output:
  pdf_document: default
  html_document: default
  word_document: default
---

#### Brief RFM description   

Recency-Frequency-Monetary distribution analysis       
- `Recency` - Nr of days since last order       
- `Frequency` - Nr of sales          
- `Monetary`  - Average value of sales         

The analysis is done based on browserid.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message =  FALSE, results = TRUE )

```

```{r load-packages, message=FALSE, echo=FALSE, warning=FALSE}
if(!require(knitr)){install.packages("knitr")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(lubridate)){install.packages("lubridate")}
if(!require(scales)){install.packages("scales")}
if(!require(tidyr)){install.packages("tidyr")}
#if(!require(gridExtra)){install.packages("gridExtra")}
if(!require(cowplot)){install.packages("cowplot")}
if(!require(grid)){install.packages("grid")}
if(!require(cluster)){install.packages("cluster")}
#if(!require(clValid)){install.packages("clValid")}
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(tibble)){install.packages("tibble")}
if(!require(stringi)){install.packages("stringi")}
```

```{r - include functions}
source('../utils/functions.R')
```

#RFM for clientid = `r params$clientid` currency = `r params$currency`   

#Distribution of browserids based on frequency, recency and monetary values


```{r - load-csv}
csvfilepath <- paste("../csv", "/",params$prefix,  "kpi.csv", sep = "")
d_kpi <- read.csv(file=csvfilepath, header=TRUE, sep=",")
```


```{r - global }
#kable(head(d_kpi, 10))
segments <- c("Hibernating", "Customers needing attention", "Potential Loyalist", "Loyal customers", "Recent Customers","Champions")
```

```{r - RFM dataset}
d_rfm <- select(d_kpi, nrofdayssincelastorder, CountOfSales, AOV, orderquarter)
d_rfm <- rename(d_rfm, recency = nrofdayssincelastorder, frequency = CountOfSales, monetary = AOV, Q = orderquarter)

```

```{r - recency global constants }
percents <- c(0, 0.25, 0.5, 0.75, 1)
title <- "Ratio of sales under given number of days" 
x <- "% of sales under the given number of days" 
y <- "Recency" 
caption <- "(in the middle - count of sales under the given percentage and max nr of days since last order)"
binwidth = 0.4
barwidth = 0.8
y_text_position = 100

```

## Recency

### Standard scales


```{r recency standard}
# 1. plot histogram boxplot summary
#plot_summary(d_rfm, d_rfm$recency, y, binwidth)

# 2. standard table summary
d_summary(d_rfm, d_rfm$recency)
quantile(d_rfm$recency)

# 3. ratio plot for standard percentage
#ratio_plot(percents, d_rfm$recency, title, x, y, caption, barwidth, y_text_position)

# 4. all summaries in table format for standard percentage
d_rfm_r <- d_kpi_feature(percents, d_rfm$recency)
d_rfm_r
```




### Observed scales
In case of Recency no need of observed scales

```{r - recency observed}
percents <- c(0, 0.25, 0.5, 0.7, 0.9, 0.95, 0.99, 0.999, 1)
# 3.
#ratio_plot(percents, d_rfm$recency, title, x, y, caption, barwidth, y_text_position)
# 2. 4.
#summary(d_rfm$recency)
#quantile(d_rfm$recency)
d_rfm_r <-d_kpi_feature(percents, d_rfm$recency)
d_rfm_r
```


## Frequency

```{r - frequency global constants}

percents <- c(0, 0.25, 0.5, 0.75, 1)
title <- "Ratio of sales under given number of days" 
x <- "Nr of Sales" 
y <- "Frequency" 
caption <- "(in the middle - )"
binwidth = 0.4
barwidth = 0.8
y_text_position = 4
```


### Standard scales


```{r frequency standard}

# 1. plot histogram boxplot summary
#plot_summary(d_rfm, d_rfm$frequency, y, binwidth)

# 2. standard table summary
d_summary(d_rfm, d_rfm$frequency)
quantile(d_rfm$frequency)

# 3. ratio plot for standard percentage
#ratio_plot(percents, d_rfm$frequency, title, x, y, caption, barwidth, y_text_position)

# 4. all summaries in table format for standard percentage
d_rfm_f <- d_kpi_feature(percents, d_rfm$frequency)
d_rfm_f
```

### Observed scales

```{r - frequency observed}
percents <- c(0, 0.9, 0.99, 0.999, 1)
# 3.
#ratio_plot(percents, d_rfm$frequency, title, x, y, caption, barwidth, y_text_position)
# 2. 4.
#summary(d_rfm$frequency)
#quantile(d_rfm$frequency)
d_rfm_r <-d_kpi_feature(percents, d_rfm$frequency)
d_rfm_r
```

## Monetary

```{r - monetary global constants}

percents <- c(0, 0.25, 0.5, 0.75, 1)
title <- "Ratio of sales under given values" 
x <- "Nr of Sales" 
y <- "Monetary" 
caption <- "(in the middle - )"
binwidth = 0.4
barwidth = 0.8
y_text_position = 9000
```


### Standard scales


```{r monetary standard}

# 1. plot histogram boxplot summary
#plot_summary(d_rfm, d_rfm$monetary, y, binwidth)

# 2. standard table summary
d_summary(d_rfm, d_rfm$monetary)
quantile(d_rfm$monetary)

# 3. ratio plot for standard percentage
#ratio_plot(percents, d_rfm$monetary, title, x, y, caption, barwidth, y_text_position)

# 4. all summaries in table format for standard percentage
d_rfm_m <- d_kpi_feature(percents, d_rfm$monetary)
d_rfm_m

```

### Observed scales

```{r - monetary observed}
percents<- c(0, 0.25, 0.5, 0.75, 0.9, 0.99, 0.999, 1)
# 3.
#ratio_plot(percents, d_rfm$monetary, title, x, y, caption, barwidth, y_text_position)
# 2. 4.
summary(d_rfm$monetary)
quantile(d_rfm$monetary)
d_rfm_r <-d_kpi_feature(percents, d_rfm$monetary)
d_rfm_r
```


## Quaterly changes in distribution of customers on recency, frequency and monetary

### Profile(browserid) categories 

Recency categories are:     
recent (recency_1): NrOfDaysSinceLastOrder < 123 (70 % of sales are less than that value)      
some_time_ago (recency_2): NrOfDaysSinceLastOrder >= 123 and NrOfDaysSinceLastOrder < 233    
long_time_ago (recency_3): NrOfDaysSinceLastOrder >= 233         

Frequency categories are:      
one_time_buyer (frequency_1): NrOfSales = 1 (70 % of sales are less than that value)         
frequent_buyer (frequency_2): NrOfSales > 1         


Monetary categories are:      
small_amount_spent (monetary_1): AOV (Average Value of Sales) < 85 (25 % of sales are less than that value)     
medium_amount_spent (monetary_2): AOV >= 85 and  AOV >= 737 (90% of the sales < 600)     
high_amount_spent (monetary_3): AOV > 737     

```{r - rfm distribution}
lrecency <- c("recent", "some_time_ago", "long_time_ago")
lfrequency <- c("frequent_buyer", "one_time_buyer")
lmonetary <- c("small_amount", "medium_amount", "high_amount")

d_rfm <- d_rfm %>%
 mutate(recency_distr = 
  ifelse(recency >= 233, lrecency[3],
  ifelse(recency <= 123 , lrecency[1],
  lrecency[2] 
  )))

d_rfm <- d_rfm %>%
 mutate(frequency_distr =
  ifelse(frequency == 1, lfrequency[2],
  lfrequency[1]
  ))

d_rfm <- d_rfm %>%
mutate(monetary_distr = 
  ifelse(monetary >= 382, lmonetary[3],
  ifelse(monetary <= 85, lmonetary[1],
  lmonetary[2] 
  )))
```


```{r - d_rfm verify 1}
#d_rfm_summary <- d_rfm  %>%
  #filter(monetary_distr == 'monetary_3' ) %>%
#  group_by(frequency_distr) %>%
#  summarise( count  = n())

#d_rfm_summary
```

```{r - d_rfm verify 2}

#d_rfm_filter <- d_rfm  %>%
#  filter(monetary >= 739 )
  

#d_rfm_filter
```


```{r - rfm distribution plot1}
# custom order recency, frequency, monetary columns 
d_rfm$recency_distr <- factor(d_rfm$recency_distr, levels=lrecency)
d_rfm$frequency_distr <- factor(d_rfm$frequency_distr, levels=lfrequency)

 p_base <- ggplot(d_rfm, aes(x = recency_distr, fill = frequency_distr)) +
  geom_bar(stat='count', position = "dodge", width = 0.8)+
  labs( title = "Distribution of customers on monetary, recency and frequency", 
        x = "", 
        y = "", 
        caption = "",
        fill = "Frequency")+
  theme(plot.title = element_text(hjust = 0.6),
      legend.text = element_text(size = 6),
        axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 9, face = "bold"),
        
      strip.text = element_text(face = "bold", size=7,lineheight=5.0),
      strip.background = element_rect(fill="lightblue", colour="black",size=.1),
      axis.text.y=element_text(hjust=1,vjust=0.5, size = 8, face = "bold"),
      strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
      panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))

p1<-p_base + facet_wrap(~ monetary_distr, nrow = 1)
p1
```
         
## Quaterly changes in distribution of customers on recency, frequency and monetary


```{r - quaterly distribution}
p2<-p_base + 
    #theme(panel.spacing = unit(0.31, "lines"))+
    facet_wrap(Q ~ monetary_distr, nrow = 2)
p2
```

##Distribution of customers on recency, frequency cluster and monetary



Firstly, a cluster comprised of recency and frequency was done using a clustering algoritm. Then a distribution on monetary values and this cluster is done.

```{r - clustering-kmeans}
# Set random seed. Don't remove this line.
set.seed(100)

d_clusters <- select(d_rfm, recency, frequency, monetary)
d_clusters <- as.data.frame(scale(d_clusters))

#d_clusters$recency<-scale(d_clusters$recency)

clusters <- kmeans(d_clusters, centers = 6, nstart = 12)
#clusters$cluster
#clusters$size
#clusters$centers
#clusters$betweens/clusters$totss
#clusters$tot.withinss/clusters$totss
#dunn_km <- dunn(clusters = clusters$cluster, Data = d_clusters, method = "euclidian")
#dunn_km

```


```{r - naming the segments}
# lengths(segments) should be equal to cluster number
df_rank <- naming_segments(clusters, segments, 6)
#df_rank

```

```{r - clustering - hierarchical}
## hierarchical clustering
#Dist <- dist(d_clusters,method="euclidean")
#clusterObj <- hclust(Dist, method="average")
#nc <- 5 ## number of clusters      
#clusters <- cutree(clusterObj,nc)
#dunn(Dist, cluster)

```


```{r - validation of clustering algorithms}
#clmethods <- c("hierarchical","kmeans")
#intern <- clValid(d_clusters, nClust = 5,
#              clMethods = clmethods, validation = "internal", maxitems = 19000, metric #= "euclidean")
# Summary
#summary(intern)

```


```{r - validation, results = FALSE, echo = FALSE, message=FALSE}
# Set random seed. Don't remove this line.
set.seed(100)

# Initialise ratio_ss
ratio_ss <- rep(0, 10)

# Finish the for-loop
for (k in 1:7) {
  
  # Apply k-means to d_clusters: school_km
  cluster_km <- kmeans(d_clusters, k, nstart = 20)
  
  # Save the ratio between of WSS to TSS in kth element of ratio_ss
  ratio_ss[k] <- cluster_km$tot.withinss / cluster_km$totss
  
}

# Make a scree plot with type "b" and xlab "k"
#plot(ratio_ss, type = "b", xlab = "k")

```
## Customer segments

Champions ::	Bought recently, buy often and spend the most!   
Loyal Customers ::	Spend good money with us often. Responsive to promotions.	    
Potential Loyalist ::	Recent customers, but spent a good amount and bought more than once.          
Recent Customers ::	Bought most recently, but not often.	   
Promising	:: Recent shoppers, but haven’t spent much.    
Customers Needing Attention ::	Above average recency, frequency and monetary values.May not have bought very recently though.	    
Hibernating	:: Last purchase was long back, low spenders and low number of orders.     	
     

```{r - merge clusters to original data adds segment names}
d_result <- cbind(d_rfm, clusters$cluster)
#rename last column
names(d_result)[length(names(d_result))]<-"cluster"

# add segment names from df_rank
d_result <- add_column(d_result, segment = "")
d_result$segment <- as.character(d_result$cluster)

for (i in 1:nrow(d_result)) {
  # match cluster from results and ranking data
  position <- match(d_result$cluster[i], df_rank$cluster) 
  d_result$segment[i] <- as.character(df_rank$segment[position])
}

d_result$segment <- factor(d_result$segment, levels = segments)

d_result_summary <- d_result  %>%
  select(segment) %>%
  group_by(segment) %>%
  summarise( size  = n())

kable(d_result_summary)
```


```{r - view clusters}
#custom order of segment
d_result$segment <- factor(d_result$segment, levels= segments)

ggplot(d_result, aes(x = recency, y = frequency, color = segment )) + 
  geom_point() +
  labs(title = 'Customer segments', x='Recency', y='Frequency')

```



```{r - rfm distribution plot based on clustering}
# custom order recency, frequency, monetary columns 
#d_rfm$recency_distr <- factor(d_rfm$recency_distr, levels=lrecency)
#d_rfm$frequency_distr <- factor(d_rfm$frequency_distr, levels=lfrequency)

 p_base_cluster <- ggplot(d_result, aes(x = segment, fill = segment)) +
  geom_bar(stat='count', position = "dodge", width = 0.8)+
  labs( title = "Customer segments on monetary values", 
        x = "", 
        y = "", 
        caption = "")+
  theme(plot.title = element_text(hjust = 0.6),
      legend.text = element_text(size = 6),
        axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 9, face = "bold"),
        
      strip.text = element_text(face = "bold", size=7,lineheight=5.0),
      strip.background = element_rect(fill="lightblue", colour="black",size=.1),
      axis.text.y=element_text(hjust=1,vjust=0.5, size = 8, face = "bold"),
      strip.text.x = element_text(margin = margin(.05, .05, 0.05, 0.05, "cm")),
      panel.grid.major = element_line(colour = "gray50", size = 0.1, linetype = "dotted"))

p_base_cluster+facet_wrap(~ monetary_distr, nrow = 1)
#p_cluster<-p_base_cluster + facet_wrap(~ monetary_distr, nrow = 1)
#p_cluster
```
